---
title: "ANLY 512-Lab1"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
```
#Intro text {.sidebar}

Summary: We can see that Johnson & Johnson is performing better in most key indicators except Price/Earning ratio while Novartis finishing a close second. Although the candlecharts indicate upward trend for Merck and Novartis as well, the Market Capitalization for J&J is significantly higher than the rest (almost twice as much). Hence I would recommend investing in J&J among these 4 stocks as it has the highest potential for short term gain

```{r}
```
# Performance Analysis of Four Pharma Stocks

Column 1 {data-width=250}
-----------------------------------------------------------------------

### Price Movement for Merck


```{r}


merck<-read.csv("C:/Users/admin/Documents/HarrisburgU/ANLY 512/MRK.csv")
merck.subset<-merck[,-7]

merck<-na.omit(merck)
library(xts)
library(magrittr)
library(dygraphs)
merck.new<-as.matrix(merck.subset)
merck.xts <- xts(merck.new[,-1], order.by=as.Date(merck.new[,1]))
m1 <- tail(merck.xts, n = 32)
dygraph(m1) %>%
  dyCandlestick()

```


### Price Movement for Pfizer

```{r}
#plot it for pfizer
pfizer<-read.csv("C:/Users/admin/Documents/HarrisburgU/ANLY 512/PFE.csv")
library(dplyr)
library(xts)
pfizer.subset<-pfizer[,-7]
pfizer.new<-as.matrix(pfizer.subset)
pfizer.xts <- xts(pfizer.new[,-1], order.by=as.Date(pfizer.new[,1]))

library(tidyverse)
library(dygraphs)


m2 <- tail(pfizer.xts, n = 32)
dygraph(m2) %>%
  dyCandlestick()

```

Column 2 {data-width=250}
-----------------------------------------------------------------------

### Price Movement for J&J
```{r}

#plot for Johnson & Johnson

jnj<-read.csv("C:/Users/admin/Documents/HarrisburgU/ANLY 512/JNJ.csv")
library(dplyr)
library(xts)
jnj.subset<-jnj[,-7]
jnj.new<-as.matrix(jnj.subset)
jnj.xts <- xts(jnj.new[,-1], order.by=as.Date(jnj.new[,1]))

m3 <- tail(jnj.xts, n = 32)
dygraph(m3) %>%
  dyCandlestick()
```

### Price Movement for Novartis

```{r}
#plot for novartis

nvs<-read.csv("C:/Users/admin/Documents/HarrisburgU/ANLY 512/NVS.cSV")
library(dplyr)
library(xts)
nvs.subset<-nvs[,-7]
nvs.new<-as.matrix(nvs.subset)
nvs.xts <- xts(nvs.new[,-1], order.by=as.Date(nvs.new[,1]))

m4 <- tail(nvs.xts, n = 32)
dygraph(m4) %>%
  dyCandlestick()
```


Column 3{data-width=500}
-----------------------------------------------------------------------

### Key Indicators
  
  
```{r}
library(quantmod)
library(plyr)
what_metrics <- yahooQF(c("Price/Sales", 
                          "P/E Ratio",
                          "Price/EPS Estimate Next Year",
                          "PEG Ratio",
                          "Dividend/Share", 
                          "Market Capitalization", "Moving Average", "Average Daily Volume", "EPS Forward"))

tickers <- c("MRK", "PFE", "JNJ", "NVS")
# Not all the metrics are returned by Yahoo.
metrics <- getQuote(paste(tickers, sep="", collapse=";"), what=what_metrics)


#Add tickers as the first column and remove the first column which had date stamps
metrics <- data.frame(Symbol=tickers, metrics[,2:length(metrics)]) 

metrics<-metrics[,-c(5,6)]


#Change colnames
colnames(metrics) <- c("Symbol", "P.E.Ratio", "P.by.EPS.Est", "Div.per.Share", "EPS.Forward")




library(tidyr)
metrics_long <- metrics %>%
  pivot_longer(cols = -Symbol, 
               names_to = "indicator", # name is a string!
               values_to = "value")     # also a string
library(ggplot2)
library(ggthemes)

ggplot(metrics_long)+
  geom_col(aes(x=Symbol, y=value))+
  facet_wrap(~indicator)+
  ggtitle("Comparison of KPIs")+
  aes(fill=indicator)+
  theme_wsj()+
  theme(legend.position = "bottom")+
  scale_fill_manual(values=c("orange", "blue", "turquoise", "purple"), guide=guide_legend(title = "Indicator", nrow = 2))+
  theme(legend.position = "bottom")
  

```

### Other Key Indicators


```{r, results='asis'}

library(quantmod)
library(plyr)
what_metrics <- yahooQF(c("Volume", "Days High",
                          "Market Capitalization", "Average Daily Volume"))

tickers <- c("MRK", "PFE", "JNJ", "NVS")
# Not all the metrics are returned by Yahoo.
other.metrics <- getQuote(paste(tickers, sep="", collapse=";"), what=what_metrics)


#Add tickers as the first column and remove the first column which had date stamps
other.metrics <- data.frame(Symbol=tickers, other.metrics[,2:length(other.metrics)]) 

#Change colnames
colnames(other.metrics) <- c("Symbol", "Vol", "Days High", "Market.Cap", "Avg.Daily.Vol")


library(kableExtra)

other.metrics %>%
  kbl() %>%
  kable_paper(full_width = F) %>%
  column_spec(5, color = "white",
              background = spec_color(other.metrics$Market.Cap, end = 0.7))
```